---
title       : Learning Regression Models
subtitle    : Interactive Multivariate Regression Learning
author      : Muhammad Owais Masood
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : mathjax       # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Multivariate Regression

1. Complex Topic : Difficult to Learn
2. Difficult to assess the impact of adding new dependent variables.
3. Solution is to provide an interactive learning APP to PLUG and PLAY the variables
4. Use Simple Dataset

--- .class #id 

## MTCARS DataSet

1. Learning MULTIVARIATE Regression through a PRE BUILT Data Set
1. Dataset used for this study was extracted from the 1974 Motor Trend US magazine
2. MPG vs 10 aspects of automobile design and performance for 32 automobiles

```{r}
data(mtcars) ; head(mtcars,2)
```

--- 
## MTCARS CONTINUED : PAIRWISE PLOT

```{r,echo=FALSE}
pairs(mpg ~ am + cyl + wt + hp , data = mtcars)
```

---
## ABOUT THE APP

1. Select the variables that you want
2. Get the Model Coefficient
3. Get the R2
4. Add/Remove Variables to Assess The Impact

---
## APPLICATION AVAILABLE ON

1. https://owaismasood.shinyapps.io/DataProject/





